### 2012-09-06 article-template.tex
Cleaned up .sty file
Cleaned up article-template.tex
Messed around with headers. Not complete yet

%% !TEX encoding = UTF-8 Unicode 
%% Author: Maarten Steenhagen / organisation: UCL
%% Created on 2012-04-25.
%% Copyright (c) 2012. All rights reserved.

\documentclass[a4paper,11pt, twosided]{article}
\usepackage{pja-article}

% Left corner subsequent pages
\thejournal{Postgraduate Journal of Aesthetics}{PJA} 
\thevolume{9}
\theissue{1}
\themonth{January}
\theyear{2012}
\thejournalinfo{http://www.pjaesthetics.org/}

\thehtitle{Literature and Sincerity} % Title in the header (no caps is fine)
\theauthor{Katy Thomas} % THESE ARE USED FOR LABELLING AS WELL
\theaffil{University of Warwick}
\thecontactd{~} % Currently not used
\theemail{k.thomas@warwick.ac.uk} % THESE ARE USED FOR LABELLING AS WELL
\firstpage{13}

\proof

\begin{document}
\pdfdetails

\maketitle{literature and sincerity}

@@

\signoff{Katy Thomas recently completed an MA in Philosophy and Literature at the University of Warwick, following a BA in English at Sussex. Currently preparing for doctoral work, she is particularly interested in theories of expression, the political impact of the arts, and the intersection of literary aesthetics and literary theory. Her literary research is focused on South American Boom and Post-Boom literature, including the \emph{testimonio} genre. Her MA dissertation sought to question the conceptual distinction between personally expressive and politically interventionary literary works.}

>>>>

%% !TEX encoding = UTF-8 Unicode 
%% Author: Maarten Steenhagen / organisation: Postgraduate Journal of Aesthetics
%% Created on 2012-04-25.
%% Modified on 2012-09-26
%% Copyright (c) 2012. All rights reserved.
\documentclass[a4paper,11pt, twoside, draft]{article}
\usepackage{pja-article}

\thejournal{Postgraduate Journal of Aesthetics}{PJA} 
\thevolume{9}
\theissue{1}
\themonth{January}
\theyear{2012}
\thejournalinfo{http://www.pjaesthetics.org/}

\thehtitle{literature and sincerity} % Title in the header (no caps is fine)
\thehauthor{katy thomas} % Author in the header (no caps is fine)
\theauthor{Katy Thomas} % THESE ARE USED FOR LABELLING AS WELL
\theaffil{University of Warwick}
\thecontactd{~} % Currently not used
\theemail{k.thomas@warwick.ac.uk} % THESE ARE USED FOR LABELLING AS WELL

\firstpage{13} % Sets the first page number
\proof {}

\begin{document}
\pdfdetails % Required to output author/title information in .PDF

\maketitle{literature and sincerity}% No caps should be used for title

@@

% The signoff command also generates the bibliography, and should not be omitted.
\signoff{Katy Thomas recently completed an MA in Philosophy and Literature at the University of Warwick, following a BA in English at Sussex. Currently preparing for doctoral work, she is particularly interested in theories of expression, the political impact of the arts, and the intersection of literary aesthetics and literary theory. Her literary research is focused on South American Boom and Post-Boom literature, including the \emph{testimonio} genre. Her MA dissertation sought to question the conceptual distinction between personally expressive and politically interventionary literary works.}
